Computer Science House Constitution

### 2019-11-01 constitution.tex
Set housing points to two
Correct Intro Members being required to pay dues during intro process
Capitalize Introductory Evaluations

This means that until the member has passed the introductory evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.

>>>>

This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
